Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] additions in introductio to type theory.

Type theory is another formalism for the foundation of mathematics, and it has become in a key instrument to study logic and proof theory.
It was proposed in 1902 to avoid the Russell's paradox and it follows
the same philosophy of constructive mathematics where the witness of
a statement is \emph{everything}. In that direction, we could say
the main actors in type theory are the statements and their proofs.
The \emph{types} are theorems and their \emph{terms} are the proofs.

Since it is a formal system, in type theory, we have a syntax and a set of derivation rules. These rules enables us to get certain kind of conclusions that we call \emph{judgments}. A judgment is a statement that says a
term has certain type.

@@

With the derivation rules we produce derivation trees inside
the judgments. These trees represent proofs of theorems.
We use such level of expressiveness for the reconstructed proofs
from the \ATPs.

% Since type theory can be seen as typed lambda calculus with dependent products,
% compute terms is basically $\beta$-reductions.
% And we

We choose a proof-assistant for type theory
because of the verification of proofs is type-checking, that is,
given a type of the theorem and the proof-term, verify that term
effectively has the type of the theorem.
Therefore, by following the Curry-Howard correspondence,

% Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
% the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:type-theory}.

>>>>

Type theory is another formalism for the foundation of mathematics, and it has become in a key instrument to study logic and proof theory.
It was proposed in 1902 to avoid the Russell's paradox and it follows
the same philosophy of constructive mathematics where the witness of
a statement is \emph{everything}. In that direction, we could say
the main actors in type theory are the statements and their proofs.
By following the Curry-Howard correspondence, we say
\emph{types} are theorems and their \emph{terms} are their proofs.

Since the type theory is formal system, we have a syntax and a set of
derivation rules. These rules enables us to derive a kind of conclusions called
\emph{judgments}. A judgment is another way a term has certain type.

@@

We produce derivation trees inside the judgments using the derivation rules. The task to verify if a proof proves a certain theorem becomes in verify if the
derivation tree of the proof has the type of the theorem. This process is known
as type-checking. This feature of type theory allow us to verify a proof
generated by \ATPs by reconstructing its proof-term to type-check the proof.
However, type theory has some limitations for proof-reconstruction as we
describe in the following section.
